Review of Group 8 by Group 1

### 2015-02-10 rmtw/a1_review/latex8.tex
Changed some things and added more comments

\Section{Introduction}
The literature review is well-written, extensive and seems to cover a lot of surrounding studies. It is good that a paper supporting the importance of personal fulfilment has been cited, since your paper almost stands and falls by this. One improvement for the Related Work section could be to write it as one text where you content drive the text instead of listing the papers one by one. This way you would get a more condensed text which is constructed around your paper.

@@

The definition of expertise is a bit too vague and ambiguous, in our opinion. You can probably replace expertise with years of experience and achieve the same results, since there should be a strong correlation between the two. The same goes for partner's skill level. It is a bit unclear from the paper what partner's skill level means. It can probably be clarified that partner's skill level is a 1-5 rating made by the other partner.

@@

\Section{Suitable Research Design}
The description of your population is clear and well-researched. It is good that you spent time to research how you find the most meaningful population, by for example leaving out inexperienced developers. One improvement to your research design section would be to, in the introduction, briefly outline your research process and describe which stages it includes and it what order they will be carried out. 
\\

@@

\Section{Other}
Below sentence does not make sense: \\
``The purpose of this survey study is to assess the impact of pair programming on personal fulfilment, controlling for expertise of developers with pair programming at mid sized software development organisations. ''

>>>>

\Section{Introduction}
The literature review is well-written, extensive and seems to cover a lot of surrounding studies. It is good that a paper supporting the importance of personal fulfilment has been cited, since your paper almost stands and falls by this. One improvement for the Related Work section could be to write it as one text where your content drives the text instead of listing the papers one by one. This way you would get a more condensed text which is constructed around your paper.

@@

The definition of expertise is a bit too vague and ambiguous, in our opinion. You can probably replace expertise with years of experience and achieve the same results, since there should be a strong correlation between the two. The same goes for partner's skill level. It is a bit unclear from the paper what partner's skill level means. It can probably be clarified that partner's skill level is a 1-5 rating made by the other partner. It also might be nice to define what you think a mid-sized team is prior to talking about how many people are at the companies. Is it 300-400, 400-500 persons etc, does this include all staff or just developers etc.

@@

\Section{Suitable Research Design}
The description of your population is clear and well-researched. It is good that you spent time to research how you find the most meaningful population, for example leaving out inexperienced developers. One improvement to your research design section would be to, in the introduction, briefly outline your research process and describe which stages it includes and in what order they will be carried out. 
\\

@@

\Section{Other}
Below sentence does not make much sense: \\
``The purpose of this survey study is to assess the impact of pair programming on personal fulfilment, controlling for expertise of developers with pair programming at mid sized software development organisations. ''
